### 2022-08-16 manuscript.Rmd
Update chunk options
Re-format LaTeX header

header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage{orcidlink}
  - \usepackage[all]{nowidow}
  - \captionsetup[figure]{belowskip=10pt,font={small,stretch=1},labelfont=bf,labelsep=period,name=Figure,textfont=normalfont}
---

@@

# Set global options
options(readr.show_col_types = FALSE)
opts_chunk$set(fig.width = 12, include = FALSE, out.width = "100%")

>>>>

header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage{orcidlink}
  - \usepackage[all]{nowidow}
  - \captionsetup[figure]{belowskip=10pt}
  - \captionsetup[figure]{font={small,stretch=1},textfont=normalfont}
  - \captionsetup[figure]{labelfont=bf,labelsep=period,name=Figure}
---

@@

# Set global options
options(readr.show_col_types = FALSE)
opts_chunk$set(
  fig.width = 12,
  include = FALSE,
  message = FALSE,
  out.width = "100%",
  warning = FALSE
)
